Concurrent Programming with CXL

### 2020-06-04 book/paper.tex
Latest version

\documentclass{report}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{amsmath}

@@

\begin{figure}
\begin{code}
\verbatiminput{triangle.cxl}
\end{code}
\caption{Computing triangle numbers.}
\label{fig:triangle}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{Up.cxl}
\end{code}
\caption{Incrementing twice in parallel.}
\label{fig:inc}
\end{figure}

@@

A name tag consists of the name of the main method of the process,
along with an optional tag specified in the \texttt{spawn} statement.
The default tag is \texttt{()}.
In Figure~\ref{fig:inc}, the created processes have name tags
\texttt{incrementer/0}, \texttt{incrementer/1}, and \texttt{main/()}.

@@

Figure~\ref{fig:incoutput} shows the output produced by running the
\texttt{Up.cxl} program.
It starts by reporting that the assertion on line 12 failed and that
\texttt{count} has value 1 instead of 0:
\texttt{Assertion failed (’assert’, ’Up.cxl’, 12, 1) 1}.
Next it reports an execution that failed this assertion.  The output has
four columns:
\begin{enumerate}
\item The name tag of the process;
\item The sequence of program counters of the CXL machine instructions that the process executed;
\item The current program counter of the process;
\item The contents of the shared memory.
\end{enumerate}

@@

\begin{figure}
\begin{code}
\verbatiminput{csbarebones.cxl}
\end{code}
\caption{A barebones critical section.}
\label{fig:csbarebones}
\end{figure}

\begin{figure}
\begin{code}
\verbatiminput{cs.cxl}
\end{code}
\caption{CXL model of a critical section.}
\label{fig:cs}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{UpLock.cxl}
\end{code}
\caption{Na\"{\i}ve implementation of a shared lock.}
\label{fig:uplock}
\end{figure}

\begin{figure}
\begin{code}
\verbatiminput{UpFlags.cxl}
\end{code}
\caption{Na\"{\i}ve use of flags to solve mutual exclusion.}
\label{fig:upflags}
\end{figure}

\begin{figure}
\begin{code}
\verbatiminput{UpTurn.cxl}
\end{code}
\caption{Na\"{\i}ve use of turn variable to solve mutual exclusion.}
\label{fig:upturn}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../Peterson.cxl}
\end{code}
\caption{Peterson's Algorithm}
\label{fig:peterson}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../PetersonProof.cxl}
\end{code}
\caption{Peterson's Algorithm with Inductive Invariant}
\label{fig:petersonproof}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../PetersonMethod.cxl}
\end{code}
\caption{Peterson's Algorithm accessed through methods.}
\label{fig:petersonmethods}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{UpTAS.cxl}
\end{code}
\caption{Mutual Exclusion using a ``spinlock'' based on test-and-set.}
\label{fig:tas}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{UpTASinv.cxl}
\end{code}
\caption{Checking invariants.}
\label{fig:tasinv}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../TAS.cxl}
\end{code}
\caption{Fixed version of Figure~\ref{fig:uplock} using test-and-set.}
\label{fig:tas2}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{UpFixed.cxl}
\end{code}
\caption{Program of Figure~\ref{fig:inc} fixed with a lock.}
\label{fig:incfixed}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../RWbusy.cxl}
\end{code}
\caption{Busy-Waiting Reader/Writer Lock implementation.}
\label{fig:rwbusy}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../RWlock.cxl}
\end{code}
\caption{Reader/Writer with Two Locks.}
\label{fig:rw2lock}
\end{figure}

@@

\begin{figure}
\begin{code}
\verbatiminput{../PCsema.cxl}
\end{code}
\caption{Bounded Buffer implementation using semaphores.}
\label{fig:boundedbuffer}
\end{figure}

>>>>

\documentclass{report}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{triangle.cxl}
\end{code}
\caption{Computing triangle numbers.}
\label{fig:triangle}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{Up.cxl}
\end{code}
\caption{Incrementing twice in parallel.}
\label{fig:inc}
\end{figure}

@@

A name tag consists of the name of the main method of the process,
along with an optional tag specified in the \texttt{spawn} statement.
The default tag is the first argument to the method.
In Figure~\ref{fig:inc}, the created processes have name tags
\texttt{incrementer/0}, \texttt{incrementer/1}, and \texttt{main/()}.

@@

Figure~\ref{fig:incoutput} shows the output produced by running the
\texttt{Up.cxl} program.
It starts by reporting that the assertion on line 9 in column 5 failed and that
\texttt{count} has value 1 instead of 0:
\texttt{Assertion failed (’assert’, ’Up.cxl’, 9, 5) 1}.
Next it reports an execution that failed this assertion.  The output has
four columns:
\begin{enumerate}
\item The name tag of the process;
\item The sequence of program counters of the CXL machine instructions that the process executed;
\item The current program counter of the process;
\item The contents of the shared memory.
\end{enumerate}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{csbarebones.cxl}
\end{code}
\caption{A barebones critical section.}
\label{fig:csbarebones}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{cs.cxl}
\end{code}
\caption{CXL model of a critical section.}
\label{fig:cs}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{UpLock.cxl}
\end{code}
\caption{Na\"{\i}ve implementation of a shared lock.}
\label{fig:uplock}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{UpFlags.cxl}
\end{code}
\caption{Na\"{\i}ve use of flags to solve mutual exclusion.}
\label{fig:upflags}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{UpTurn.cxl}
\end{code}
\caption{Na\"{\i}ve use of turn variable to solve mutual exclusion.}
\label{fig:upturn}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../Peterson.cxl}
\end{code}
\caption{Peterson's Algorithm}
\label{fig:peterson}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../PetersonProof.cxl}
\end{code}
\caption{Peterson's Algorithm with Inductive Invariant}
\label{fig:petersonproof}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../PetersonMethod.cxl}
\end{code}
\caption{Peterson's Algorithm accessed through methods.}
\label{fig:petersonmethods}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{UpTAS.cxl}
\end{code}
\caption{Mutual Exclusion using a ``spinlock'' based on test-and-set.}
\label{fig:tas}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{UpTASinv.cxl}
\end{code}
\caption{Checking invariants.}
\label{fig:tasinv}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../TAS.cxl}
\end{code}
\caption{Fixed version of Figure~\ref{fig:uplock} using test-and-set.}
\label{fig:tas2}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{UpFixed.cxl}
\end{code}
\caption{Program of Figure~\ref{fig:inc} fixed with a lock.}
\label{fig:incfixed}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../RWbusy.cxl}
\end{code}
\caption{Busy-Waiting Reader/Writer Lock implementation.}
\label{fig:rwbusy}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../RWlock.cxl}
\end{code}
\caption{Reader/Writer with Two Locks.}
\label{fig:rw2lock}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../PCsema.cxl}
\end{code}
\caption{Bounded Buffer implementation using semaphores.}
\label{fig:boundedbuffer}
\end{figure}
